Quantum Interval-Valued Probability: Measurement and Probability

### 2017-08-26 prop_iop.tex
prop_iop.tex \subsection{Expectation Values for Classical IVPMs} Updating...

\begin{definition}[Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}]\label{def:Choquet}~
\begin{itemize}
\item Consider a classical IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
\item We still decompose a random variable~$X$ into step functions, but
we separate the positive and negative terms and write like $\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}+\sum_{i=1}^{N^{+}}x_{i}^{+}\mathbf{1}_{E_{i}^{+}}$,
i.e., 
\begin{equation}
x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
\end{equation}
 and $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
are all disjoint.
\item Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$ and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-\mu^{*}\left(E_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
\end{itemize}
Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
\begin{equation}
\int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\,.\label{eq:interval-expectation}
\end{equation}
\end{definition}

\noindent The following lemma shows our definition is exactly the
same as in the literature.

@@

\noindent Similar to equation~(\ref{eq:expectation}), equation~(\ref{eq:interval-expectation})
can be considered as weighted average of the possible outcomes of
$X$ as well, despite the ``weight''
\begin{equation}
\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\subseteq\left[\mul\left(E_{i}^{s}\right),\mur\left(E_{i}^{s}\right)\right]=\bar{\mu}\left(E_{i}^{s}\right)\textrm{ for }s\in\left\{ +,-\right\} 
\end{equation}
is tighter than the interval-valued probability of the corresponding
event. Since only one event can happen at once, we don't have to be
so pessimistic to accumulate all possible fuzziness together, and
expect $\sum_{i=1}^{N}x_{i}\bar{\mu}\left(E_{i}^{s}\right)$ to happen.

The Choquet integral has many desirable properties. For example, it
has the same range as all expectation value in the core, and it generalizes
the Lebesgue integral.

Notice that $\left[1.7,1.8\right]$ in example~\ref{ex:expectation}
is just the right-hand side of equation~(\ref{eq:Rosenmuller}).
Let compute the left-hand side of equation~(\ref{eq:Rosenmuller})
in table~\ref{table:Choquet} and see they are equal.
\begin{table}
\begin{tabular}{|c|c|c|c|}
\hline 
$i$ & 1 & 2 & 3\tabularnewline
\hline 
\hline 
$x_{i}^{+}$ & 1 & 2 & \tabularnewline
\hline 
$E_{i}^{+}$ & $E$ & $\overline{E}$ & \tabularnewline
\hline 
$E_{i}^{+\prime}$ & $E$ & $\Omega$ & $\emptyset$\tabularnewline
\hline 
$\mul\left(E_{i}^{+\prime}\right)$ &  &  & \tabularnewline
\hline 
 &  &  & \tabularnewline
\hline 
 &  &  & \tabularnewline
\hline 
 &  &  & \tabularnewline
\hline 
\end{tabular}\caption{\label{table:Choquet}}
\end{table}

>>>>

\begin{definition}[Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}]\label{def:Choquet}~
\begin{itemize}
\item Consider a classical IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
\item We still decompose a random variable~$X$ into step functions, but
we separate the positive and negative terms and write like $\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}+\sum_{i=1}^{N^{+}}x_{i}^{+}\mathbf{1}_{E_{i}^{+}}$,
i.e., 
\begin{equation}
x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
\end{equation}
 and $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
are all disjoint.
\item Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$ and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-\mu^{*}\left(E_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
\end{itemize}
Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
\begin{equation}
\int X\rmd\bar{\mu}=\left[\sum_{i=1}^{N^{+}}x_{i}^{+}\Delta\mul\left(E_{i}^{+\prime}\right)+\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mur\left(E_{i}^{-\prime}\right),\sum_{i=1}^{N^{+}}x_{i}^{+}\Delta\mur\left(E_{i}^{+\prime}\right)+\sum_{i=1}^{N^{-}}x_{i}^{-}\Delta\mul\left(E_{i}^{-\prime}\right)\right]\,.\label{eq:interval-expectation}
\end{equation}
\end{definition}

\begin{table}
\caption{\label{table:Choquet}
\[
\int X\rmd\bar{\mu}=\left[1\cdot0.3+2\cdot0.7,1\cdot0.2+2\cdot0.8\right]=\left[1.7,1.8\right]\,.
\]
}

\begin{indented}
\item\begin{tabular}{|c|c|c|c|c|c|c|c|} 
\br 
$i$ & $x_{i}^{+}$ & $E_{i}^{+}$ & $E_{i}^{+\prime}$ & $\mul\left(E_{i}^{+\prime}\right)$ & $\Delta\mul\left(E_{i}^{+\prime}\right)$ & $\mur\left(E_{i}^{+\prime}\right)$ & $\Delta\mur\left(E_{i}^{+\prime}\right)$\tabularnewline 
\mr 
$1$ & $1$ & $E$ & $\Omega$ & $1$ & $0.3$ & $1$ & $0.2$\tabularnewline 
\mr 
$2$ & $2$ & $\overline{E}$ & $\overline{E}$ & $0.7$ & $0.7$ & $0.8$ & $0.8$\tabularnewline 
\mr 
$3$ &  &  & $\emptyset$ & $0$ &  & $0$ & \tabularnewline 
\br 
\end{tabular}
\end{indented}
\end{table}
Table~\ref{table:Choquet} follows the definition to compute $\int X\rmd\bar{\mu}$.
Notice that equation~(\ref{eq:interval-expectation}) looks complex.
On the one hand, it would be a little bit easier to think its right-hand
side as 
\begin{equation}
\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\,,\label{eq:interval-expectation-1}
\end{equation}
$\Delta\mul\left(E_{i}^{s\prime}\right)$ can be larger than $\Delta\mur\left(E_{i}^{s\prime}\right)$
as in the second row in table~\ref{table:Choquet}. Therefore, if
we want to use this notation, we need to stick to this convention
that not reverse the two ends of intervals, even if the left-end is
larger than the right-end. On the other hand, similar to equation~(\ref{eq:expectation}),
equation~(\ref{eq:interval-expectation-1}) can be considered as
weighted average of the possible outcomes of $X$ as well, despite
the ``weight''
\begin{equation}
\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\subseteq\left[\mul\left(E_{i}^{s}\right),\mur\left(E_{i}^{s}\right)\right]=\bar{\mu}\left(E_{i}^{s}\right)\textrm{ for }s\in\left\{ +,-\right\} 
\end{equation}
is tighter than the interval-valued probability of the corresponding
event. This makes it easier to remember.

Also, $\left[1.7,1.8\right]$ in example~\ref{ex:expectation} is
exactly the same as the expectation value computed in table~\ref{table:Choquet}.
This nature property can be generated to the following theorem.

The next lemmas shows our definition is exactly the same as in the
literature, and is consistent with the CRVPM.

@@
